Neural Textures make Better Simulators ``I can't believe it's not real!"

### 2022-06-12 CORL/example.tex
Added method overview

\newcommand{\toB}{_{1\dots B}}
\newcommand{\toBL}{_{1\dots B,1\dots L}}
\newcommand{\toL}{_{1\dots L}}

@@

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}

@@

@@

	\begin{figure}[H]
		\begin{center}
			% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
			\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
		\end{center}
		\caption{
			We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
			To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
			This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
			$B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
			Inputs are on the left, and outputs are on the right.
			The dashed arrows indicate losses between nodes.
			Although $\pi_{1\dots B}$ and $\hat{p}_{1\dots B}$ look similar, they are not identical. 
			$\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
			% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
			% TODO: Use variables instead of 3,4
			% TODO: Make the text larger and easier to read
			% TODO: Simplify the diagram?
		}
		\label{fig:main_diagram}
	\end{figure}

@@

Our similarity losses are the sum of L2 distance and negative multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}. For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1. Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - msssim(x,y)$.

>>>>

\newcommand{\toB}{_{1\dots B}}
% \newcommand{\toBL}{_{1\dots B,\text{ } 1\dots L}}
\newcommand{\toBL}{_{1\dots B, 1\dots L}}
\newcommand{\toL}{_{1\dots L}}

@@

% \usepackage{corl_2022} % Use this for the initial submission.
\usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}

@@

Domain A and B
p hat
s hat

@@

\begin{figure}[H]
	\begin{center}
		% \includegraphics[width=400pt]{../images/main_diagram_condensed.pdf}
		\includegraphics[width=400pt]{../images/main_diagram_condensed_with_domains.pdf}
	\end{center}
	\caption{
		% We use differentiable rendering paired with unpaired image translation to consistently= transform synthetic scenes into realistic images.
		% To ensure all objects look consistent in different positions and views, we learn the albedo of each object's surface by using a learnable latent texture.
		% This texture is parametrized as an image generated by an MLP which is fed Fourier features, as shown in figure \ref{fig:learnable_textures}.
		% $B$ is the batch size, and $L$ is the number of different labels (which is also the number of learnable textures).
		This figure is an overview of how TRITON works, showing all submodules and losses.
		Inputs are on the left, and outputs are on the right.
		The dashed arrows indicate losses between nodes.
		Although $\pi\toB$ and $\ph\toB$ look similar, they are not identical - $\lTR$ encourages them to look as similar as possible.
		% $\pi$ is simply projected textures, whereas $\hat{p}$ has been run through an image translator, allowing it to have shadows and specularities.
		% TODO: Come up with a tour of this diagram in this caption. Also maybe make it larger?
		% TODO: Use variables instead of 3,4
		% TODO: Make the text larger and easier to read
		% TODO: Simplify the diagram?
	}
	\label{fig:main_diagram}
\end{figure}

	In this section, we describe how TRITON works to translate images from domain A (simulation) to domain B (photos) while maintaining surface consistency. 
	TRITON has four main components: a neural texture, an image translator, and two surface consistency losses.
	\begin{enumerate}
		\item{
			Neural Textures $\tau\toL$: Given an input scene $s$ depicting 3d objects with labels $1\dots L$, we project learnable RGB textures $\tau\toL$ to their surfaces to obtain projection $\pi$. 
			These neural textures are represented implicitly by a neural network that maps UV values to RGB values, and are learned jointly with the image translator.
			\begin{equation}
				\pi=\tau\toL(s)
			\end{equation}
			We then concatenate the scenes with the projections channelwise to obtain images from domain A: $\ppis \in A$.
		}
		\item{
			Bidirectional Image Translator $T$: $\Tab$ translates images from domain A to domain B, and $\Tba$ translates images from domain B to domain A.
			\begin{equation}
				\ph=\Tab(\pis)\ \ \ \text{ and }\ \ \ \ppish=\Tba(p)
			\end{equation}
			$T$ is a variation of MUNIT, and inherits adversarial losses $\ell_{adv}$, as well cycle consistency losses $\ell_{cyc}$ and reconstruction losses $\ell_{rec}$.
		}
		\item {
			Unprojection Consistency Loss $\lUC$: To keep the object surfaces consistent between a batch of $B$ scenes, we impose a pixel-wise similarity loss between these surfaces by warping them back into a common texture space using the UV and label values contained in the original scene. 
			\begin{equation}
				u\toBL=\text{unproject}(\ph\toB,s\toB)\ \ \ \text{ and } \ \ \ \lTR \Rightarrow u_1 \approx u_2 \dots \approx u_B
			\end{equation}
		}
		\item{
			Texture Realism Loss $\lTR$: To encourage the neural textures to look as realistic as possible, we try to make the projections look like the final output. 
			\begin{equation}
				\lTR \Rightarrow \pi \approx \ph
			\end{equation}
			As it turns out, $\lTR$ is sufficiently powerful loss to generate surface-consistent translations even without $\lUC$, although the results are better when both losses are used.
		}

	\end{enumerate}

@@

Our similarity losses are the sum of L2 distance and negative multi scale structural image similarity (MS-SSIM), introduced in \citep{msssim}. For our purposes, MS-SSIM is a metric that measures the similarity of two BCHW tensors on a scale from 0 to 1. Given two tensors $x$ and $y$, their similarity loss is $\mu\left((x-y)^2\right) - \text{msssim}(x,y)$.
